%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{ifthen}
\usepackage{calc}
% \usepackage{times}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{list}{}{% \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar


%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            % includefoot, % Uncomment to put page number above margin
            marginparwidth=1.15in,     % Length of section titles
            marginparsep=.1in,       % Space between titles and text
%            margin=1in,               % 1 inch margins
						top = .7in,
						left = .8in,
						right = .8in,
						bottom = .6in,
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
%                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
\hypersetup{colorlinks=true,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%
% the picture will be flush right across from the name.
\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
\renewcommand{\section}[1]{\pagebreak[3]%
    \hyphenpenalty=10000%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\halfblankline}{\quad\vspace{-0.4\baselineskip}\pagebreak[3]}
% \newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\blankline}{\quad\vspace{-0.1\baselineskip}\pagebreak[3]}
\newcommand{\secspace}{\\ \quad\vspace{-0.6\baselineskip}\pagebreak[3]}
% \newcommand{\halfblankline}{}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

% For \url{SOME_URL}, links SOME_URL to the url SOME_URL
\providecommand*\url[1]{\href{#1}{#1}}
% Same as above, but pretty-prints SOME_URL in teletype fixed-width font
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}

% For \email{ADDRESS}, links ADDRESS to the url mailto:ADDRESS
\providecommand*\email[1]{\href{mailto:#1}{#1}}
% Same as above, but pretty-prints ADDRESS in teletype fixed-width font
%\renewcommand*\email[1]{\href{mailto:#1}{\texttt{#1}}}

%\providecommand\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%\providecommand\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    \TeX}}
\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    \TeX}}
\providecommand\Matlab{\textsc{Matlab}}


\newcommand{\awardedby}[1]{\hfill\mbox{}\linebreak[0]\hspace*{\fill} \mbox{\textit{#1}}}
\newcommand{\publication}[3]{#2. \textit{#1}. #3.}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ADJUST MARGINS
%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{.875in}




%%%%%%%%%%%%%%%%%%%%%%%%% Names %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\biswa}{\underline{B. Paria}}
\newcommand{\pabitra}{P. Mitra}
\newcommand{\partha}{P. Bhowmick}
\newcommand{\ambedkar}{A. Dukkipati}
\newcommand{\annervaz}{K.M. Annervaz}
\newcommand{\anirban}{A. Santara}
\newcommand{\prabir}{P.K. Biswas}
\newcommand{\sanjoy}{S. Pratihar}
\newcommand{\avisek}{A. Lahiri}
\newcommand{\barnabas}{B. P\'oczos}
\newcommand{\samy}{K. Kandasamy}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newboolean{iscustom}
\setboolean{iscustom}{false}
\setboolean{iscustom}{true}

\begin{document}

\hspace*{-\marginparsep minus \marginparwidth}%
\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
    {\large \bfseries BISWAJIT PARIA} \\
    [.2\baselineskip]%
    San Francisco, CA, USA 94103\\
    \textit{Web:} 
      \href{https://biswajitsc.github.io}{https://biswajitsc.github.io},
    \hspace{0.15in}
    % \textit{Phone:} +1 412 620 3004,
    % \hspace{0.15in}
    \textit{E-mail:} \href{mailto:bparia@cs.cmu.edu}{biswajitsc@gmail.com}
       \\[-.55\baselineskip]%
           \rule{\columnwidth}{1pt}
\end{minipage}


% CV begins here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.2in}

\section{Research Interests}
Bayesian Optimization, Decision Making under Uncertainty, Time Series Forecasting using NNs, Deep Learning
~\secspace



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\textbf{Carnegie Mellon University}, Pittsburgh, PA \hfill Aug 2017 - Jul 2022\\*
M.S., Ph.D. in Machine Learning. \hfill \textit{Advisors:} \href{https://www.cs.cmu.edu/~bapoczos/}{Barnab\'{a}s P\'oczos}, \href{https://www.cs.cmu.edu/~schneide/}{Jeff Schneider}\\*
\ifthenelse{\boolean{iscustom}}{
\textit{Fall 21 GPA: 4.05 (A+: 4.33, A: 4.0).} \\*
}{}
\halfblankline

\textbf{Indian Institute of Technology Kharagpur}, India \hfill Jul 2012 - Apr 2017 \\*
5-year Bachelors and Masters in Computer Science and Engineering\\*
\ifthenelse{\boolean{iscustom}}{
\textit{GPA 9.80$\,$/$\,$10.00}, highest in class\\*
}{}
\secspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Professional Experience %%%%%%%%%%%%%%%%%%%%%%%%%
% \ifthenelse{\boolean{iscustom}}{
\section{Professional Experience}
Software Engineer III \hfill Google, Mountain View, CA. Jul 2022 - current\\*
\textbf{Google Ads}\\*
\textit{Designing, training, and serving machine learning models for efficient and accurate predictions for Google Ads.}
\\\halfblankline

Summer Research Intern \hfill Google Research, Mountain View, CA. May - Oct 2020\\*
\textbf{Hierarchical Time-Series Forecasting} \textit{with} Abhimanyu Das, Amr Ahmed \\*
\textit{Proposed a scalable machine learning method for forecasting of time series arranged in an hierarchy
which resulted in improved forecast accuracy.}
\\ \halfblankline

Summer Research Intern \hfill Snap Research, Los Angeles, CA. May - Aug 2018\\*
\textbf{Sparse Representations for Fast Retrieval} \textit{with} Ian En-Hsu Yen, Ning Xu \\*
\textit{Proposed a machine learning approach to sparsify image embeddings resulting in
upto 50$\times$ speed up in image retrieval using sparse matrix multiplication operations.}
\\ \halfblankline

Summer Research Intern \hfill
U. of Southern California, Los Angeles, CA. May - Jul 2015\\*
\textbf{Interpretability of Learned Features for Clinical Time Series} \textit{with} Prof. Yan Liu\\*
\textit{Proposed a strategy to interpret features learned by a deep neural network trained on
clinical time series data.}

% Summer Research Intern \hfill
% IISc\footnote{Indian Institute of Science} and Accenture Tech. Labs. Bengaluru, India, 2016\\*
% \textbf{Natural Language Inference} \textit{with} Ambedkar Dukkipati (IISc) and Annervaz K.M. (ATL)\\*
% \textit{Proposed a deep learning model using LSTMs and attention for Natural Language Inference.}
% }{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Honours and Awards %%%%%%%%%%%%%%%%%%%%%%%

\section{Honours \& Awards}
Prime Minister of India Gold Medal \awardedby{IIT Kharagpur, 2017}\\*
\textit{Awarded to the highest ranking student of the graduating class at IIT Kharagpur.}
\\ \halfblankline
  
Viterbi-India Scholar \awardedby{2015}\\*
\textit{Funded summer internship at Viterbi School of Engineering, University of Southern California.}
\\ \halfblankline
  
ACM ICPC World Finalist (Team \emph{BitBees}) \awardedby{2015}\\*
\textit{One of 7 teams from India at the International Collegiate Programming Competition.}
\\ \halfblankline

%  \textbf{Jagadish Bose National Science Talent Search (JBNSTS) Scholar} \hfill 2013\\
%   Awarded to 30 candidates in the state of West Bengal.
%   \SmallEntryGap
  
Indian National Physics Olympiad (INPhO) Awardee \awardedby{2012}\\*
\textit{Among the top 30 candidates in India.}\\*
\textit{Attended the Indian team selection camp for the International Physics Olympiad.}
\\ \halfblankline

Indian National Mathematical Olympiad (INMO) Awardee \awardedby{2010 - 2012}\\*
\textit{Among the top 30 candidates in India.}\\*
\textit{Attended the Indian team selection camp for the International Mathematics Olympiad.}
\\ \halfblankline
  
Kishore Vaigyanik Protsahan Yojana (KVPY) Scholar 
\hfill \textit{2011}\\*
\textit{Awarded by the Dept. of Science and Technology, India for exceptional aptitude in basic sciences. Achieved the 7th rank in India.}
\\ \halfblankline
  
Australian Mathematics Competition (AMC) Gold Medallist \hfill \textit{2009}\\*
\textit{Awarded by the Australian Mathematics Trust. One of 23 medallists in the world.}
\\ \halfblankline
\secspace


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Papers %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Papers}

A. Das, W. Kong, \biswa, R. Sen. \emph{Dirichlet Proportions Model for Hierarchically Coherent Probabilistic Forecasting}. Uncertainty in Artificial Intelligence (UAI), 2023. [\href{https://arxiv.org/abs/2204.10414}{arxiv}, \href{https://proceedings.mlr.press/v216/das23b.html}{paper}].
\\ \halfblankline

S. Kumar, \biswa, Y. Tsvetkov. \emph{Gradient-Based Constrained Sampling from Language Models}. Empirical Methods in Natural Language Processing (EMNLP), 2022. [\href{https://preview.aclanthology.org/emnlp-22-ingestion/2022.emnlp-main.144.pdf}{paper}, \href{http://128.84.21.203/abs/2205.12558}{arxiv}]
\\ \halfblankline

V. Mehta, \biswa, J. Schneider, S. Ermon, W. Neiswanger. \emph{An Experimental Design Perspective on Model-Based Reinforcement Learning}. International Conference on Learning Representations (ICLR), 2022. Preliminary version at EcoRL Workshop @ NeurIPS, 2021.
[\href{https://arxiv.org/abs/2112.05244}{arxiv}, \href{https://openreview.net/pdf?id=0no8Motr-zO}{paper}]
\\ \halfblankline

\biswa, R. Sen, A. Ahmed, A. Das. \emph{Hierarchically Regularized Deep Forecasting}. 2021. [\href{https://arxiv.org/abs/2106.07630}{arxiv}]
\\ \halfblankline

\biswa, W. Neiswanger, R. Ghods, J. Schneider, \barnabas. \emph{Cost-Aware Bayesian Optimization via Information Directed Sampling}. Real World Experiment Design and Active Learning Workshop @ ICML, 2020. [\href{https://realworldml.github.io/files/cr/29_Cost_Aware_BO_ICML_2020_Workshop.pdf}{paper}]
\\ \halfblankline

\samy, K. R. Vysyaraju, W. Neiswanger, \biswa, C. R. Collins, J. Schneider, \barnabas, E. P. Xing. \emph{Tuning Hyperparameters without Grad Students: Scalable and Robust Bayesian Optimisation with Dragonfly}. Journal of Machine Learning Research (JMLR), 2020. [\href{https://arxiv.org/abs/1903.06694}{arxiv}, \href{https://jmlr.csail.mit.edu/papers/volume21/18-223/18-223.pdf}{paper}]
\\ \halfblankline

\biswa, C.K. Yeh, I.E.H. Yen, N. Xu, P. Ravikumar, \barnabas. \emph{Minimizing FLOPs to Learn Efficient Sparse Representations}. International Conference on Learning Representations (ICLR), 2020. [\href{https://openreview.net/pdf?id=SygpC6Ntvr}{paper}, \href{https://github.com/biswajitsc/sparse-embed}{code}]
\\ \halfblankline

\biswa, \samy, \barnabas. \emph{A Flexible Framework for Multi-Objective Bayesian Optimization using Random Scalarizations}. Uncertainty in Artificial Intelligence (UAI), 2019.
[oral presentation, \href{https://arxiv.org/abs/1805.12168}{arxiv}, \href{http://auai.org/uai2019/proceedings/papers/267.pdf}{paper}]
\\ \halfblankline

\biswa, \annervaz, \ambedkar, A. Chatterjee, S. Podder. \emph{A Neural Architecture Mimicking Humans End-to-End for Natural Language Inference}. 2016. [\href{https://arxiv.org/abs/1611.04741}{arxiv}]
\\ \halfblankline

\avisek, \biswa, \prabir. \emph{Forward Stagewise Additive Model for Collaborative Multiview Boosting}. IEEE Transactions in Neural Networks and Learning Systems, 2016. [\href{https://arxiv.org/abs/1608.01874}{arxiv}, \href{https://ieeexplore.ieee.org/abstract/document/7778196}{paper}]
\\ \halfblankline

% A. Guha, M.S. Pydi, \biswa, \ambedkar. \emph{Analytic Connectivity in General Hypergraphs}. \arxiv{2017}. (\href{https://arxiv.org/abs/1701.04548}{arxiv})

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Teaching %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section {Teaching}

\textbf{Teaching Assistantships:} \\
Advanced Machine Learning \hfill CMU, Spring 2019 \\
Convex Optimization \hfill CMU, Fall 2018 \\
Deep Learning \hfill IIT Kharagpur, Spring 2017 \\
Machine Learning \hfill IIT Kharagpur, Fall 2016 \\
\\ \halfblankline

\textbf{Math Olympiad Teaching} \hfill 2012 \& 2013\\
Taught number theory and combinatorics to high school students
\\ \halfblankline


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Programming Lang %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Programming Skills} \emph{Proficient:} Python, \emph{Familiar:} C++, bash\\
\emph{Libraries:} Tensorflow, PyTorch, numpy, sklearn, JAX
\secspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Relevant courses %%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relevant Courses}
Advanced Introduction to Machine Learning \hfill CMU, Fall 2017\\
Intermediate Statistics \hfill CMU, Fall 2017\\
Statistical Machine Learning \hfill CMU, Spring 2017\\
Probabilistic Graphical Models \hfill CMU, Spring 2017\\
Advanced Statistical Theory \hfill CMU, Fall 2018\\
Martingales \hfill CMU, Fall 2018\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \ifthenelse{\boolean{iscustom}}{
% \section{References}
% \href{https://www.cs.cmu.edu/~bapoczos/}{Barnab\'{a}s P\'oczos} (bapoczos@cs.cmu.edu), PhD advisor\\
% \href{https://www.cs.cmu.edu/~schneide/}{Jeff Schneider} (jeff4@andrew.cmu.edu), PhD advisor
% }{}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
